---
output:
  html_document:
    keep_md: true
    theme: simplex
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    toc_depth: 4
    df_print: paged
    code_folding: hide
fontsize: 12pt
---

```{r, include=FALSE}
library(tidyverse)
library(readxl)
library(GGally)
library(broom)
library(ggfortify)
library(skimr)
library(lubridate)
library(janitor) ## excel_numeric_to_date()



options(scipen = 20)

knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      fig.align = "center",
                      fig.width = 8)

```



```{r, include=FALSE}
sheets <- readxl::excel_sheets("KPMG_VI_New_raw_data_update_final.xlsx")[-1]


for (sheet in sheets) {
    assign(as.character(sheet),
           read_xlsx("KPMG_VI_New_raw_data_update_final.xlsx", sheet = sheet, skip = 1))
}

```


# Data Cleaning

## Transactions

I don' think keeping cancelled orders is going to help us find lucrative customers. 

```{r}
Transactions <- Transactions %>% 
  filter(order_status != "Cancelled")
```

I am going to use `list_price` - `standard_cost` = `profit` as a candidate response variable. Also I want to try `profit_per_interaction` variable as a response as well. So I am removing the observations which miss `standard_cost`.

```{r}
Transactions <- Transactions %>% 
  filter(!is.na(standard_cost))
```

I am not going to remove observations with missing `online_order`values because their `list_price` and `standard_cost` values are intact.

This is the table that holds potential response variables. 

```{r}
response_table <- Transactions %>% 
  mutate(profit = list_price - standard_cost) %>% 
  group_by(customer_id) %>% 
  summarise(
    total_profit = sum(profit),
    n_transaction = n()
  ) %>% 
  mutate(profit_per_transaction = total_profit / n_transaction)
```

The number of transactions seems like a nice candidate for Poisson Regression but Profits per Transaction has nice distribution except for very high values.

```{r}
response_table %>% 
  ggplot(aes(n_transaction))+
  geom_bar()

response_table %>% 
  ggplot(aes(total_profit))+
  geom_histogram(color = "white")

response_table %>% 
  ggplot(aes(profit_per_transaction))+
  geom_histogram(color = "white")
```

## Customer Demographic and Address

These tables hold our predictors.

There were some inconsistencies with the gender variable. For now I am only adjusting typos and "F", "M" type of errors. I am keeping gender "U" because it might have some systematic information. Though the amount of observations are very low.

```{r}
CustomerDemographic <- CustomerDemographic %>% 
  mutate(gender = ifelse(gender %in% c("F", "Femal"), "Female", gender)) %>%
  mutate(gender = ifelse(gender == "M", "Male", gender))
```

I am dropping some useless columns for modeling process. 

```{r}
CustomerDemographic <- CustomerDemographic %>% 
  select(-default, -first_name, -last_name, -deceased_indicator,)
```

Adjusting job titles.

```{r}
CustomerDemographic %>% skim()
  filter(is.na(job_title)) %>% 
  select(job_title, job_industry_category)
```


```{r}
CustomerDemographic %>% 
  filter(job_industry_category == "n/a" & !is.na(job_title))
```




































































