---
title: "Sales and Customers"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(readxl)
library(GGally)
library(broom)
library(ggfortify)
library(skimr)
library(lubridate)
library(janitor) ## excel_numeric_to_date()
library(scales)
library(patchwork)

theme_set(theme_minimal(base_size = 15))

options(scipen = 20)

knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      fig.align = "center",
                      fig.width = 8)
```

```{r, include=FALSE}
sheets <- readxl::excel_sheets("../Task_2/KPMG_VI_New_raw_data_update_final.xlsx")[-1]


for (sheet in sheets) {
    assign(as.character(sheet),
           read_xlsx("../Task_2/KPMG_VI_New_raw_data_update_final.xlsx", sheet = sheet, skip = 1))
}

Transactions <- Transactions %>% 
  filter(order_status != "Cancelled")

Transactions <- Transactions %>% 
  filter(!is.na(standard_cost))

Transactions <- Transactions %>% 
  mutate(profit = list_price - standard_cost,
         product_first_sold_date = convert_to_date(product_first_sold_date))

```

```{r, include=FALSE}
CustomerDemographic <- CustomerDemographic %>% 
  mutate(gender = ifelse(gender %in% c("F", "Femal"), "Female", gender)) %>%
  mutate(gender = ifelse(gender == "M", "Male", gender))

CustomerDemographic <- CustomerDemographic %>% 
  select(-default, -first_name, -last_name, -deceased_indicator)

## Missing Values for variable job_title
CustomerDemographic %>% 
  pull(job_title) %>% is.na() %>% sum()
## Missing Values for variable job_industry_category
CustomerDemographic %>% 
  filter(job_industry_category == "n/a") %>% nrow()

CustomerDemographic <- CustomerDemographic %>% 
  mutate(job_title = str_remove(job_title, regex(" [IV]+")))

CustomerDemographic <- CustomerDemographic %>% 
  filter(!is.na(job_title))

CustomerDemographic <- CustomerDemographic %>% 
  filter(!is.na(tenure)) 

CustomerDemographic <- CustomerDemographic %>% 
  mutate(DOB = convert_to_date(DOB))

CustomerDemographic %>% 
  slice_min(order_by = DOB, n = 5)

CustomerDemographic <- CustomerDemographic %>% 
  filter(customer_id != 34)

CustomerDemographic <- CustomerDemographic %>% 
  mutate(age = as.integer((ymd("2017-06-01") - DOB) / 365.25))

CustomerAddress <- CustomerAddress %>% 
  mutate(state = ifelse(state == "New South Wales", "NSW", state),
         state = ifelse(state == "Victoria", "VIC", state)) 

Customer_Joined <- CustomerDemographic %>% 
  inner_join(CustomerAddress, by = "customer_id") %>% 
  select(-country)

Transactions <- Customer_Joined %>% 
  inner_join(Transactions, by = "customer_id") 

names(Transactions)
```

# Profits by Goods

## Column Brands {data-width=400}

### Profits by Brands

```{r}
p1 <- Transactions %>% 
  group_by(brand) %>% 
  summarise(
    sum_profit = sum(profit),
    n = n(),
    profit_per_n = sum_profit / n
  ) %>% 
  ggplot(aes(sum_profit, reorder(brand, sum_profit), fill = brand))+
  geom_col(show.legend = F, alpha = 0.8)+
  scale_fill_brewer(palette = "Set2")+
  scale_x_continuous(labels = scales::dollar_format())+
  labs(y = NULL, x = "Total Profit")
```

```{r}
p2 <- Transactions %>% 
  group_by(brand) %>% 
  summarise(
    sum_profit = sum(profit),
    n = n(),
    profit_per_n = sum_profit / n
  ) %>% 
  ggplot(aes(profit_per_n, reorder(brand, profit_per_n), fill = brand))+
  geom_col(show.legend = F, alpha = 0.8)+
  scale_fill_brewer(palette = "Set2")+
  scale_x_continuous(labels = scales::dollar_format())+
  labs(y = NULL, x = "Profits per Transaction")
```

```{r, fig.width=7, fig.height=10}
p1 / p2
```


## Column Product Properties {data-width=300, .tabset}

### Profits by Product Size

```{r}
p1 <- Transactions %>% 
  group_by(product_size) %>% 
  summarise(
    sum_profit = sum(profit),
    n = n(),
    profit_per_n = sum_profit / n
  ) %>% 
  ggplot(aes(sum_profit, reorder(product_size, sum_profit), fill = product_size))+
  geom_col(show.legend = F, alpha = 0.8)+
  scale_fill_brewer(palette = "Set2")+
  scale_x_continuous(labels = scales::dollar_format(),breaks = c(1e6, 3e6, 5e6))+
  labs(y = NULL, x = "Total Profit")
```


```{r}
p2 <- Transactions %>% 
  group_by(product_size) %>% 
  summarise(
    sum_profit = sum(profit),
    n = n(),
    profit_per_n = sum_profit / n
  ) %>% 
  ggplot(aes(profit_per_n, reorder(product_size, profit_per_n), fill = product_size))+
  geom_col(show.legend = F, alpha = 0.8)+
  scale_fill_brewer(palette = "Set2")+
  scale_x_continuous(labels = scales::dollar_format())+
  labs(y = NULL, x = "Profits per Transaction")
```

```{r, fig.width=7, fig.height=10}
p1 / p2
```

### Profits by Product Class

```{r}
p1 <- Transactions %>% 
  group_by(product_class) %>% 
  summarise(
    sum_profit = sum(profit),
    n = n(),
    profit_per_n = sum_profit / n
  ) %>% 
  ggplot(aes(sum_profit, reorder(product_class, sum_profit), fill = product_class))+
  geom_col(show.legend = F, alpha = 0.8)+
  scale_fill_brewer(palette = "Set2")+
  scale_x_continuous(labels = scales::dollar_format())+
  labs(y = NULL, x = "Total Profit")

p2 <- Transactions %>% 
  group_by(product_class) %>% 
  summarise(
    sum_profit = sum(profit),
    n = n(),
    profit_per_n = sum_profit / n
  ) %>% 
  ggplot(aes(profit_per_n, reorder(product_class, profit_per_n), fill = product_class))+
  geom_col(show.legend = F, alpha = 0.8)+
  scale_fill_brewer(palette = "Set2")+
  scale_x_continuous(labels = scales::dollar_format())+
  labs(y = NULL, x = "Profits per Transaction")
```

```{r, fig.width=7, fig.height=10}
p1 / p2
```


### Profits by Product Line

```{r}
p1 <- Transactions %>% 
  group_by(product_line) %>% 
  summarise(
    sum_profit = sum(profit),
    n = n(),
    profit_per_n = sum_profit / n
  ) %>% 
  ggplot(aes(sum_profit, reorder(product_line, sum_profit), fill = product_line))+
  geom_col(show.legend = F, alpha = 0.8)+
  scale_fill_brewer(palette = "Set2")+
  scale_x_continuous(labels = scales::dollar_format())+
  labs(y = NULL, x = "Total Profit")

p2 <- Transactions %>% 
  group_by(product_line) %>% 
  summarise(
    sum_profit = sum(profit),
    n = n(),
    profit_per_n = sum_profit / n
  ) %>% 
  ggplot(aes(profit_per_n, reorder(product_line, profit_per_n), fill = product_line))+
  geom_col(show.legend = F, alpha = 0.8)+
  scale_fill_brewer(palette = "Set2")+
  scale_x_continuous(labels = scales::dollar_format())+
  labs(y = NULL, x = "Profits per Transaction")
```


```{r, fig.width=7, fig.height=10}
p1 / p2
```


## Column Time {data-width=300}

### Amount of Profits per Month

```{r}
Transactions %>% 
  mutate(month = month(transaction_date, label = TRUE, locale = "english")) %>% 
  group_by(month) %>% 
  summarise(
    sum_profit = sum(profit),
    n = n(),
    profit_per_n = sum_profit / n
  ) %>% 
  ggplot(aes(month, sum_profit))+
  geom_col(fill ="steelblue", alpha = 0.8)+
  geom_line(aes(group = 1), linewidth = 1.5, alpha = 0.8)+
  geom_point(color = "gray", size = 3, alpha = 0.8)+
  scale_y_continuous(labels = scales::dollar_format())+
  labs(y = "Profits", x = NULL)
```

### Number of Transactions per Month

```{r}
Transactions %>% 
  mutate(month = month(transaction_date, label = TRUE, locale = "english")) %>% 
  group_by(month) %>% 
  summarise(
    sum_profit = sum(profit),
    n = n(),
    profit_per_n = sum_profit / n
  ) %>% 
  ggplot(aes(month, n))+
  geom_col(fill ="steelblue", alpha = 0.8)+
  geom_line(aes(group = 1), linewidth = 1.5, alpha = 0.8)+
  geom_point(color = "gray", size = 3, alpha = 0.8)+
  labs(y = "Amount of Transactions", x = NULL) 

```


# Profits by Demographics

## Job Titles {data-width=700}

### Best and Worst 15 Profitable Job Titles

```{r}
p1 <- Transactions %>% 
  group_by(job_title) %>% 
  summarise(
    sum_profit = sum(profit),
    n = n(),
    profit_per_n = sum_profit / n
    
  ) %>% 
  slice_max(order_by = profit_per_n, n = 15) %>% 
  bind_rows(
    Transactions %>% 
  group_by(job_title) %>% 
  summarise(
    sum_profit = sum(profit),
    n = n(),
    profit_per_n = sum_profit / n
    
  ) %>% 
  slice_min(order_by = profit_per_n, n = 15)
  ) %>% 
  ggplot(aes(sum_profit, reorder(job_title, sum_profit), fill = sum_profit))+
  geom_col(show.legend = F, alpha = 0.8)+
  scale_fill_gradient(low = "darkgreen", high = "green")+
  scale_x_continuous(labels = scales::dollar_format())+
  labs(y = NULL, x = "Total Profit")

p2 <- Transactions %>% 
  group_by(job_title) %>% 
  summarise(
    sum_profit = sum(profit),
    n = n(),
    profit_per_n = sum_profit / n
    
  ) %>% 
  slice_max(order_by = profit_per_n, n = 15) %>% 
  bind_rows(
    Transactions %>% 
  group_by(job_title) %>% 
  summarise(
    sum_profit = sum(profit),
    n = n(),
    profit_per_n = sum_profit / n
    
  ) %>% 
  slice_min(order_by = profit_per_n, n = 15)
  ) %>% 
  ggplot(aes(profit_per_n, reorder(job_title, profit_per_n), fill = profit_per_n))+
  geom_col(show.legend = F, alpha = 0.8)+
  scale_fill_gradient(low = "darkgreen", high = "green")+
  scale_x_continuous(labels = scales::dollar_format())+
  labs(y = NULL, x = "Profit per Transaction")
```

```{r, fig.width=16, fig.height=10}
p1+p2
```


## Other Information {data-width=300}

### Profits by State

```{r}
p1 <- Transactions %>% 
  group_by(state) %>% 
  summarise(
    sum_profit = sum(profit),
    n = n(),
    profit_per_n = sum_profit / n
  ) %>% 
  ggplot(aes(sum_profit, reorder(state, sum_profit), fill = state))+
  geom_col(show.legend = F, alpha = 0.7)+
  scale_x_continuous(labels = scales::dollar_format(), breaks = c(1e6, 2.5e6, 4e6))+
  scale_fill_brewer(palette = "Set2")+
  labs(y = NULL, x = "Total Profits")

p2 <- Transactions %>% 
  group_by(state) %>% 
  summarise(
    sum_profit = sum(profit),
    n = n(),
    profit_per_n = sum_profit / n
  ) %>% 
  ggplot(aes(profit_per_n, reorder(state, profit_per_n), fill = state))+
  geom_col(show.legend = F, alpha = 0.7)+
  scale_x_continuous(labels = scales::dollar_format())+
  scale_fill_brewer(palette = "Set2")+
  labs(y = NULL, x = "Profit per Transaction")

p1/p2
  
```

### Profits by the status of owning a car

```{r}
p1 <- Transactions %>% 
  group_by(owns_car) %>% 
  summarise(
    sum_profit = sum(profit),
    n = n(),
    profit_per_n = sum_profit / n
  ) %>% 
  ggplot(aes(sum_profit, reorder(owns_car, sum_profit), fill = owns_car))+
  geom_col(show.legend = F, alpha = 0.7)+
  scale_x_continuous(labels = scales::dollar_format(), breaks = c(1e6, 2.5e6, 4e6))+
  scale_fill_brewer(palette = "Set2")+
  labs(y = NULL, x = "Total Profits")

p2 <- Transactions %>% 
  group_by(owns_car) %>% 
  summarise(
    sum_profit = sum(profit),
    n = n(),
    profit_per_n = sum_profit / n
  ) %>% 
  ggplot(aes(profit_per_n, reorder(owns_car, profit_per_n), fill = owns_car))+
  geom_col(show.legend = F, alpha = 0.7)+
  scale_x_continuous(labels = scales::dollar_format())+
  scale_fill_brewer(palette = "Set2")+
  labs(y = NULL, x = "Profit per Transaction")

p1/p2
  
```
















